Compositional Certified Resource Bounds\ifshort{\vspace{-.15cm}}{}

### 2014-07-07 paper/main.tex
typo

The small-step semantics is standard, except that it tracks the
resource consumption of a program.  The semantics is parametric in the
resource of interest for the user of our system.  We achieve this
independence by parameterizing evaluations with a resource
\emph{metric} $M$; a tuple of nine rational numbers, one map $M_e :
\text{Expr} \to \Q$ from expressions to rational numbers, and one map
$M_t : \Z \to \Q$ from integers to rational numbers
%
\iffull{.$$
M = (
M_a,
M_b,
M_r,
M_u,
M_f,
M_l,
M_c^1,
M_c^2,
M_s,
M_e(E),
M_t(n)
)
$$}{$M_a$, $M_b$, $M_r$, $\ldots\;$.

>>>>

The small-step semantics is standard, except that it tracks the
resource consumption of a program.  The semantics is parametric in the
resource of interest for the user of our system.  We achieve this
independence by parameterizing evaluations with a resource
\emph{metric} $M$; a tuple of nine rational numbers \ifshort{$M_a$, $M_b$, $M_r$, $\ldots$}{}, one map $M_e :
\text{Expr} \to \Q$ from expressions to rational numbers, and one map
$M_t : \Z \to \Q$ from integers to rational numbers.
%
\iffull{$$
M = (
M_a,
M_b,
M_r,
M_u,
M_f,
M_l,
M_c^1,
M_c^2,
M_s,
M_e(E),
M_t(n)
)
$$}{
